An Automatic Verification Framework for Software Configurations

### 2016-05-10 OSDI/learner.tex
update Q

Note that the formalism relies on Algorithm~\ref{alg:plearn}. The algorithm considers both typed templates and
untyped specifications. As a similar iteration logic is used for both, an $opt$ flag distinguishes between the two situations.
constructRule in Algorithm~\ref{alg:crules} refers to the creation of a rule from a tuple of entries, 
$m = (e_1, e_2, \ldots, e_i, \ldots, e_{n-1})$.
The rule creation is formally represented as $m(k(e_1), k(e_2), \ldots, k(e_i), \ldots, k(e_{n-1}))$. 
In order to determine if the rule satisfied, the relation associated with $m(v(e_1), v(e_2), \ldots, v(e_i), \ldots, v(e_{n-1}))$ is evaluated for truth.
The rule can be template-generated, for instance {\tt max\_connections} > {\tt mysql.max\_persistent}, or
it can be untyped-specification-generated rule, for instance the ordering that {\tt recode.so} must come before 
{\tt mysql.so}.

For typed templates, we first filter and examine entries associated with a particular type, and then check if
the template is satisfied over appropriately typed argument entries in the rest of the file. We do something similar for
untyped specifications.

>>>>

Note that the formalism relies on Algorithm~\ref{alg:plearn}. The algorithm considers both typed templates and
untyped specifications. As a similar iteration logic is used for both, an $opt$ flag distinguishes between the two situations.
constructRule in Algorithm~\ref{alg:crules} refers to the creation of a rule from a tuple of entries, 
$m = (e_1, e_2, \ldots, e_i, \ldots, e_{n-1})$.
The rule creation is formally represented as $m(k(e_1), k(e_2), \ldots, k(e_i), \ldots, k(e_{n-1}))$. 
In order to determine if the rule satisfied, the relation associated with $m(v(e_1), v(e_2), \ldots, v(e_i), \ldots, v(e_{n-1}))$ is evaluated for truth.
The rule can be template-generated, for instance {\tt max\_connections} > {\tt mysql.max\_persistent}, or
it can be untyped-specification-generated, for instance the ordering that {\tt recode.so} must come before 
{\tt mysql.so}.

The candidate entry set $Q$ in Algorithm~\ref{alg:plearn} 
differs for the two cases.
For typed templates, due to typing restrictions, 
we must first filter and examine entries associated with the same type, in order to check that 
the template is satisfied over appropriately typed argument entries. This manifests itself via $Q = filter(F,\tau)$
in Algorithm~\ref{alg:plearn}. For
untyped specifications, we do not need to adhere to this typing restriction, so we simply set $Q = F$.
